---
title: "2020-03-23 Week 3 Notebook"
author: "Jon Page"
Last Updated: date()
output:
  html_document:
    df_print: paged
  word_document: default
Date: 23/03/2020
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(cache = TRUE)
rm(list=ls()) # Clear workspace
graphics.off() # This closes all of R's graphics windows.
cat("\f") # Clear console
library(rstudioapi) # Source rstudioapi to set working directory as needed
library(rjags) # Source rjags for Bayesian analysis
library(ggplot2) # Source ggplot2 to plot results
library(gridExtra) # Source gridExtra for better plots
library(DT) # Source DT for datatable
library(dplyr) # Source dplyr for percent_rank
library(ncdf4)
```
***
# Introduction

This notebook is to track my work in the week commencing 23/03/20.

Following Zoom with Martin and Gab, the below are my targets for this week:

1. Take FLUXNET data from one site and test it OOS
 + Model NEE as function of precip, VPD and Temp
 + Run the SAM approach over a few years and then see how the model works for
 the following years
 + I could investigate whether the 3-6 model works for it at all.
2. Sort out working from home
3. Read and produce a "BIG" question along with some hypotheses to test within
this question's framework

***

# BIG QUESTION:

### To what extent does the productivity of grasslands depend on antecedent climate and how is this influenced by eCO~2~?

1. **Which antecedent effects are most important?**

Precipitation will be seen to have the longest historical period due to the 
extended time periods over which soil moisture varies. However, it will be seen
that temperature and vapour pressure deficit will also have an impact on a more
recent timescale.

2. **What timescales do lags operate over?**

The timescale of lags is very dependent on the climate variable being examined.
However, overall, it will be important to consider the previous ~5 years when
attempting to explain grassland productivity. Since plants exposed to eCO~2~ 
have a greater capacity for production, I expect the influence of antecedent 
effects to become greater as plants are more able to take advantage of any increase
in resources.

3. **How does the role of antecedent effects change based on the prevailing climate 
at a site?**

The importance of lagged climatic variables will vary based on the ecosystem
but across grasslands, antecedent precipitation will consistently be the most 
influential historical influence. This is due to the majority of grasslands being
water-limited. This will not change significantly under eCO~2~ as water savings 
in grassland are offset by the greater climatic variability.

4. **How do extreme events interact with the role of lags in grasslands ecosystems?**

Extreme events will produce longer-lasting impacts that propogate through the 
productivity response over wider timespans than the average years. This however
will be mitigated under climate change as enhanced WUE and higher productivity
provide a cushioning effect.

***
# netCDF Files

First up is accessing the netCDF files saved at the below link and finding which
ones are from grassland sites

/srv/ccrc/data04/z3509830/Fluxnet_data/All_flux_sites_processed_PLUMBER2/Post-processed_PLUMBER2_outputs

https://fluxnet.fluxdata.org/sites/site-list-and-pages/ has a list of the sites
by IGBP classification for the FLUXNET 2015 files. 

https://fluxnet.fluxdata.org/data/la-thuile-dataset/ This page has the list for
the La Thuile sites. No La Thuile datasets for grassland sites are over 10 years 
of length (or more than about 5).

Similarly, http://www.ozflux.org.au/monitoringsites/ shows that the 2 sites from
OzFlux that had longer time series of data were not grasslands. 

US-Var from FLUXNET 2015 is a grassland site with the longest data record 
available of 14 years. 

US-Wkg has 10 years of data and was used instead (for some inexplicable reason)

The below commands were used to copy the Met and Flux files from the storm 
servers to my PC:

```{bash Flux Files, eval = FALSE}
scp z5293113@maelstrom.ccrc.unsw.edu.au:/srv/ccrc/data04/z3509830/Fluxnet_data/All_flux_sites_processed_PLUMBER2/Post-processed_PLUMBER2_outputs/Nc_files/Flux/US-Wkg_2005-2014_FLUXNET2015_Flux.nc .

scp z5293113@maelstrom.ccrc.unsw.edu.au:/srv/ccrc/data04/z3509830/Fluxnet_data/All_flux_sites_processed_PLUMBER2/Post-processed_PLUMBER2_outputs/Nc_files/Met/US-Wkg_2005-2014_FLUXNET2015_Met.nc .
```

We now have to extract the data and turn it into the format we want:

```{r Netcdf Manipulation}

name = "US-Wkg_2005-2014_FLUXNET2015_"

Met = nc_open(paste0(name,"Met.nc"))
Flux = nc_open(paste0(name,"Flux.nc"))

time = ncvar_get(Met,"time")
Tair = ncvar_get(Met,"Tair")
Precip = ncvar_get(Met,"Precip")
VPD = ncvar_get(Met,"VPD")
NEE = ncvar_get(Flux,"NEE")

ncatt_get(Met, "time")
time_from = substr(ncatt_get(Met, "time")$units, 15, 33)
time <- as.POSIXct(time, origin=time_from)

nc_close(Met)
nc_close(Flux)

# Define unit conversions
SEC_TO_30MIN = 1800
KEL_TO_CEL = -273.15

# Create data frame with the units converted
# Precip is now in mm
# Tair is now in Celsius
df <- data.frame(time, NEE, Tair+KEL_TO_CEL,Precip*SEC_TO_30MIN,VPD)
colnames(df)<- c("time","NEE","Tair","Precip","VPD")


df_day <- df %>%
      mutate(day=as.Date(time, format="%Y-%m-%d")) %>%
      group_by(day) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))

df_month <- df_day %>%
      mutate(month=format(as.Date(df_day$day),"%Y-%m")) %>%
      group_by(month) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))

# Create our Precip input matrix
Precip = data.frame(matrix(df_month$Precip,ncol = 12, byrow = TRUE))
colnames(Precip) <- c("ppt1","ppt2","ppt3","ppt4","ppt5","ppt6","ppt7","ppt8","ppt9","ppt10","ppt11","ppt12")

# Create the NEE input matrix

df_day$Year = format(df_day$day,"%Y")
NEE = aggregate(df_day['NEE'],by=df_day['Year'],sum)
```




Important differences from the code replicating Ogle et al:

1. I will NOT consider the precipitation events of the current year - Ogle et al
showed that these were insignificant for their site and they are also considered
under the monthly weights
2. I will NOT set the weights of Oct/Nov/Dec of the current year to zero - since
we are using flux-derived NEE rather than harvested biomass, this is no longer
relevant.
3. I WILL consider weights for monthly mean temp and VPD. 
4. Assuming that all sites have the same length of Precip data and NEE data, I
have had to amend the code which previously assumed that we always had Nlag prior
years of Precip for the first year of NPP data


```{r Model run for all time blocks, include=TRUE}
source("SAMFunction.R")
timeblock = SpringBlock(3)
Nlag = timeblock$Nlag
block = timeblock$block
NEE = NEE[-(1:Nlag),]
# For the timeblock created, run the model
SAM(Precip,NEE,Nlag,block,prior=FALSE)

```




```{r}
load("SAM_posterior_3_6_20200325_152051.Rdata")
library(ggplot2)
library(gridExtra) # Source gridExtra for better plots
NPPobs = data.frame(Year=1:nrow(NEE)+2006,
                    NPP_obs = NEE[,2])
NPPmod = data.frame(Year=1:length(SAM_posterior_3_6_20200325_152051$NPPmod$mean)+2009,
                    NPP_mod = SAM_posterior_3_6_20200325_152051$NPPmod$mean,
                    NPP_modmin = SAM_posterior_3_6_20200325_152051$NPPmod$min,
                    NPP_modmax = SAM_posterior_3_6_20200325_152051$NPPmod$max)
plot3 <- ggplot(NPPobs) +
  geom_line(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2) +
  geom_point(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2,na.rm=TRUE) +
  geom_ribbon(data=NPPmod, aes(x=Year, ymin=NPP_modmin, ymax=NPP_modmax), fill="grey70", alpha=0.4) +
  geom_line(data=NPPmod,aes(Year,NPP_mod)) +
  theme_bw() +
  theme(axis.line=element_line(colour = "black"),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    panel.background=element_blank()) 
grid.arrange(plot3)
```

```{r}
# Assemble the dataframe for spring/non-spring
plotWeights = data.frame("Weights"=as.vector(t(SAM_posterior_3_6_20200325_152051$monthlyWeights$mean)),
                         "YearIntoPast"=rep(0:2,each=12),
                         "Month"=rep(c("Dec","Nov","Oct","Sep", "Aug","Jul",
                                       "Jun", "May","Apr","Mar","Feb","Jan"),3))
# Assign the factors
plotWeights$Month = factor(plotWeights$Month, levels = c("Jan","Feb","Mar","Apr",
                                                         "May","Jun","Jul","Aug",
                                                         "Sep","Oct","Nov","Dec"))
# Create plot ready for grid.assign
plot1 <- ggplot(plotWeights,aes(x=YearIntoPast,y=Weights,fill=Month)) +
      geom_bar(stat="identity", position=position_dodge(), linetype = "solid",size=0.5,color="black") +
      facet_grid(.~YearIntoPast,scales = "free_x",switch = "x", space = "free_y") +
      ggtitle(paste0("3 year lag, spring/non-spring (R2 = ",
                     signif(SAM_posterior_3_6_20200325_152051$R2,2), ", DIC = ",
                     signif(SAM_posterior_3_6_20200325_152051$DIC,4), ", MAE = ",
                     signif(SAM_posterior_3_6_20200325_152051$MAE,4),")"))
grid.arrange(plot1)
```



We have 10 years of Precip and NEE data from FLUXNET - however, because we are
looking at a lag of 3 years, we effectively only have 7 years of NEE data.
This is an exceptionally short data set. 

NOTE, the above results are from only 500 samples. This will have reduced the 
accuracy quite a bit.

I may look at the longest data set available, no matter what the ecosystem is.

I did the above for the dataset US-Ha1 - it's awful. This is a deciduous
broadleaf forest... you'd think there should be some correlation between precip
and NEE... maybe soil moisture/routing depth/slower response time of tree growth
mean that precipitation isn't such an important driver? Hmmm...

```{r}
source("NCExtraction.R")
load("SAM_posterior_3_6_20200325_163324.Rdata")
Flux = NetCDFExtract("US-Ha1_1992-2012_FLUXNET2015")
library(ggplot2)
library(gridExtra) # Source gridExtra for better plots
NPPobs = data.frame(Year=1:nrow(Flux$NEE)+1992,
                    NPP_obs = Flux$NEE[,2])
NPPmod = data.frame(Year=1:length(SAM_posterior_3_6_20200325_163324$NPPmod$mean)+1995,
                    NPP_mod = SAM_posterior_3_6_20200325_163324$NPPmod$mean,
                    NPP_modmin = SAM_posterior_3_6_20200325_163324$NPPmod$min,
                    NPP_modmax = SAM_posterior_3_6_20200325_163324$NPPmod$max)
plot3 <- ggplot(NPPobs) +
      geom_line(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2) +
      geom_point(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2,na.rm=TRUE) +
      geom_ribbon(data=NPPmod, aes(x=Year, ymin=NPP_modmin, ymax=NPP_modmax), fill="grey70", alpha=0.4) +
      geom_line(data=NPPmod,aes(Year,NPP_mod)) +
      theme_bw() +
      theme(axis.line=element_line(colour = "black"),
            panel.grid.major=element_blank(),
            panel.grid.minor=element_blank(),
            panel.border=element_blank(),
            panel.background=element_blank()) 


# Assemble the dataframe for spring/non-spring
plotWeights = data.frame("Weights"=as.vector(t(SAM_posterior_3_6_20200325_163324$monthlyWeights$mean)),
                         "YearIntoPast"=rep(0:2,each=12),
                         "Month"=rep(c("Dec","Nov","Oct","Sep", "Aug","Jul",
                                       "Jun", "May","Apr","Mar","Feb","Jan"),3))
# Assign the factors
plotWeights$Month = factor(plotWeights$Month, levels = c("Jan","Feb","Mar","Apr",
                                                         "May","Jun","Jul","Aug",
                                                         "Sep","Oct","Nov","Dec"))
# Create plot ready for grid.assign
plot1 <- ggplot(plotWeights,aes(x=YearIntoPast,y=Weights,fill=Month)) +
      geom_bar(stat="identity", position=position_dodge(), linetype = "solid",size=0.5,color="black") +
      facet_grid(.~YearIntoPast,scales = "free_x",switch = "x", space = "free_y") +
      ggtitle(paste0("3 year lag, spring/non-spring (R2 = ",
                     signif(SAM_posterior_3_6_20200325_163324$R2,2), ", DIC = ",
                     signif(SAM_posterior_3_6_20200325_163324$DIC,4), ", MAE = ",
                     signif(SAM_posterior_3_6_20200325_163324$MAE,4),")"))
grid.arrange(plot1, plot3)

```

We also tested US-Var. We see a similar issue here - the modelled NPP is failing
to pick up the temporal variability in the observations and we are getting a 
very poor R2 as a result. 

Maybe precipitation alone isn't enough at these sites?
Maybe a longer dataset is needed?

I will test with the Ogle data to see how the model deals with that.

 We load the data and run the model for the spring/non-spring method of time
 blocking
```{r  Load Ogle Data}
# Load Ogle data
Precip = read.table("data/dataset3.csv",header=TRUE,stringsAsFactors = FALSE)

# Load NPP data 
NPP = read.table("data/dataset2.csv",header=TRUE,stringsAsFactors = FALSE)
NPP = NPP[,1:3]

source("SAMFunction.R")
timeblock = SpringBlock(3)
Nlag = timeblock$Nlag
block = timeblock$block
# For the timeblock created, run the model
SAM(NPP,Precip,Nlag,block,prior=FALSE)
```


Plot the output against the observed
```{r}
load("SAM_posterior_3_6_20200327_141610.Rdata")
NPPobs = data.frame(Year=1:nrow(NPP)+1938,
                    NPP_obs = NPP[,2])
NPPmod = data.frame(Year=1:length(SAM_posterior_3_6_20200327_141610$NPPmod$mean)+1938,
                    NPP_mod = SAM_posterior_3_6_20200327_141610$NPPmod$mean,
                    NPP_modmin = SAM_posterior_3_6_20200327_141610$NPPmod$min,
                    NPP_modmax = SAM_posterior_3_6_20200327_141610$NPPmod$max)
plot3 <- ggplot(NPPobs) +
  geom_line(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2) +
  geom_point(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2,na.rm=TRUE) +
  geom_ribbon(data=NPPmod, aes(x=Year, ymin=NPP_modmin, ymax=NPP_modmax), fill="grey70", alpha=0.4) +
  geom_line(data=NPPmod,aes(Year,NPP_mod)) +
  theme_bw() +
  theme(axis.line=element_line(colour = "black"),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    panel.background=element_blank()) 

# Assemble the dataframe for spring/non-spring
plotWeights = data.frame("Weights"=as.vector(t(SAM_posterior_3_6_20200327_141610$monthlyWeights$mean)),
                         "YearIntoPast"=rep(0:2,each=12),
                         "Month"=rep(c("Dec","Nov","Oct","Sep", "Aug","Jul",
                                       "Jun", "May","Apr","Mar","Feb","Jan"),3))
# Assign the factors
plotWeights$Month = factor(plotWeights$Month, levels = c("Jan","Feb","Mar","Apr",
                                                         "May","Jun","Jul","Aug",
                                                         "Sep","Oct","Nov","Dec"))
# Create plot ready for grid.assign
plot1 <- ggplot(plotWeights,aes(x=YearIntoPast,y=Weights,fill=Month)) +
      geom_bar(stat="identity", position=position_dodge(), linetype = "solid",size=0.5,color="black") +
      facet_grid(.~YearIntoPast,scales = "free_x",switch = "x", space = "free_y") +
      ggtitle(paste0("3 year lag, spring/non-spring (R2 = ",
                     signif(SAM_posterior_3_6_20200327_141610$R2,2), ", DIC = ",
                     signif(SAM_posterior_3_6_20200327_141610$DIC,4), ", MAE = ",
                     signif(SAM_posterior_3_6_20200327_141610$MAE,4),")"))
grid.arrange(plot1, plot3)
```


This doesn't look bad.

We test again but this time with a standard time block of one per month.

```{r}
# Load Ogle data
Precip = read.table("data/dataset3.csv",header=TRUE,stringsAsFactors = FALSE)

# Load NPP data 
NPP = read.table("data/dataset2.csv",header=TRUE,stringsAsFactors = FALSE)
NPP = NPP[,1:3]

source("SAMFunction.R")
block = matrix(1:36,nrow=3,byrow=TRUE)
Nlag = 3
# For the timeblock created, run the model
SAM(NPP,Precip,Nlag,block,prior=FALSE)
```

Plot again 

```{r}
load("SAM_posterior_3_36_20200327_145005.Rdata")
NPPobs = data.frame(Year=1:nrow(NPP)+1938,
                    NPP_obs = NPP[,2])
NPPmod = data.frame(Year=1:length(SAM_posterior_3_36_20200327_145005$NPPmod$mean)+1938,
                    NPP_mod = SAM_posterior_3_36_20200327_145005$NPPmod$mean,
                    NPP_modmin = SAM_posterior_3_36_20200327_145005$NPPmod$min,
                    NPP_modmax = SAM_posterior_3_36_20200327_145005$NPPmod$max)
plot3 <- ggplot(NPPobs) +
  geom_line(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2) +
  geom_point(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2,na.rm=TRUE) +
  geom_ribbon(data=NPPmod, aes(x=Year, ymin=NPP_modmin, ymax=NPP_modmax), fill="grey70", alpha=0.4) +
  geom_line(data=NPPmod,aes(Year,NPP_mod)) +
  theme_bw() +
  theme(axis.line=element_line(colour = "black"),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    panel.background=element_blank()) 

# Assemble the dataframe for spring/non-spring
plotWeights = data.frame("Weights"=as.vector(t(SAM_posterior_3_36_20200327_145005$monthlyWeights$mean)),
                         "YearIntoPast"=rep(0:2,each=12),
                         "Month"=rep(c("Dec","Nov","Oct","Sep", "Aug","Jul",
                                       "Jun", "May","Apr","Mar","Feb","Jan"),3))
# Assign the factors
plotWeights$Month = factor(plotWeights$Month, levels = c("Jan","Feb","Mar","Apr",
                                                         "May","Jun","Jul","Aug",
                                                         "Sep","Oct","Nov","Dec"))
# Create plot ready for grid.assign
plot1 <- ggplot(plotWeights,aes(x=YearIntoPast,y=Weights,fill=Month)) +
      geom_bar(stat="identity", position=position_dodge(), linetype = "solid",size=0.5,color="black") +
      facet_grid(.~YearIntoPast,scales = "free_x",switch = "x", space = "free_y") +
      ggtitle(paste0("Ogle 3 year lag, 36 blocks (R2 = ",
                     signif(SAM_posterior_3_36_20200327_145005$R2,2), ", DIC = ",
                     signif(SAM_posterior_3_36_20200327_145005$DIC,4), ", MAE = ",
                     signif(SAM_posterior_3_36_20200327_145005$MAE,4),")"))
grid.arrange(plot1, plot3)
```

Ok, so the model is now working. The output is relatively close to the observed
but not ridiculously so. We also have feasible monthly weights.

Let's run it again for the Netflux data - note the input style has changed.

```{r Netcdf Manipulation 2}

name = "US-Wkg_2005-2014_FLUXNET2015_"

Met = nc_open(paste0(name,"Met.nc"))
Flux = nc_open(paste0(name,"Flux.nc"))

time = ncvar_get(Met,"time")
Tair = ncvar_get(Met,"Tair")
Precip = ncvar_get(Met,"Precip")
VPD = ncvar_get(Met,"VPD")
NEE = ncvar_get(Flux,"NEE")

ncatt_get(Met, "time")
time_from = substr(ncatt_get(Met, "time")$units, 15, 33)
time <- as.POSIXct(time, origin=time_from)

nc_close(Met)
nc_close(Flux)

# Define unit conversions
SEC_TO_30MIN = 1800
KEL_TO_CEL = -273.15

# Create data frame with the units converted
# Precip is now in mm
# Tair is now in Celsius
df <- data.frame(time, NEE, Tair+KEL_TO_CEL,Precip*SEC_TO_30MIN,VPD)
colnames(df)<- c("time","NEE","Tair","Precip","VPD")


df_day <- df %>%
      mutate(day=as.Date(time, format="%Y-%m-%d")) %>%
      group_by(day) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))

df_month <- df_day %>%
      mutate(month=format(as.Date(df_day$day),"%Y-%m")) %>%
      group_by(month) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))


# Create the NEE input matrix

df_day$Year = format(df_day$day,"%Y")
NEE = aggregate(df_day['NEE'],by=df_day['Year'],sum)
NEE$YearID = 1:nrow(NEE)

# Create our Precip input matrix
Precip = data.frame(NEE$Year,matrix(df_month$Precip,ncol = 12, byrow = TRUE))
colnames(Precip) <- c("Year","ppt1","ppt2","ppt3","ppt4","ppt5","ppt6","ppt7","ppt8","ppt9","ppt10","ppt11","ppt12")

```

```{r Model Run}


source("SAMFunction.R")
block = matrix(1:36,nrow=3,byrow=TRUE)
Nlag = 3
# For the timeblock created, run the model
SAM(NEE[-(1:3),],Precip,Nlag,block,prior=FALSE)
```


```{r Plot Wkg}
load("SAM_posterior_3_36_20200327_155054.Rdata")
NPPobs = data.frame(Year=1:nrow(NEE)+2004,
                    NPP_obs = NEE[,2])
NPPmod = data.frame(Year=1:length(SAM_posterior_3_36_20200327_155054$NPPmod$mean)+2007,
                    NPP_mod = SAM_posterior_3_36_20200327_155054$NPPmod$mean,
                    NPP_modmin = SAM_posterior_3_36_20200327_155054$NPPmod$min,
                    NPP_modmax = SAM_posterior_3_36_20200327_155054$NPPmod$max)
plot3 <- ggplot(NPPobs) +
  geom_line(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2) +
  geom_point(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2,na.rm=TRUE) +
  geom_ribbon(data=NPPmod, aes(x=Year, ymin=NPP_modmin, ymax=NPP_modmax), fill="grey70", alpha=0.4) +
  geom_line(data=NPPmod,aes(Year,NPP_mod)) +
  theme_bw() +
  theme(axis.line=element_line(colour = "black"),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    panel.background=element_blank()) 

# Assemble the dataframe for spring/non-spring
plotWeights = data.frame("Weights"=as.vector(t(SAM_posterior_3_36_20200327_155054$monthlyWeights$mean)),
                         "YearIntoPast"=rep(0:2,each=12),
                         "Month"=rep(c("Dec","Nov","Oct","Sep", "Aug","Jul",
                                       "Jun", "May","Apr","Mar","Feb","Jan"),3))
# Assign the factors
plotWeights$Month = factor(plotWeights$Month, levels = c("Jan","Feb","Mar","Apr",
                                                         "May","Jun","Jul","Aug",
                                                         "Sep","Oct","Nov","Dec"))
# Create plot ready for grid.assign
plot1 <- ggplot(plotWeights,aes(x=YearIntoPast,y=Weights,fill=Month)) +
      geom_bar(stat="identity", position=position_dodge(), linetype = "solid",size=0.5,color="black") +
      facet_grid(.~YearIntoPast,scales = "free_x",switch = "x", space = "free_y") +
      ggtitle(paste0("3 year lag, spring/non-spring (R2 = ",
                     signif(SAM_posterior_3_36_20200327_155054$R2,2), ", DIC = ",
                     signif(SAM_posterior_3_36_20200327_155054$DIC,4), ", MAE = ",
                     signif(SAM_posterior_3_36_20200327_155054$MAE,4),")"))
grid.arrange(plot1, plot3)
```

This is way too accurate for me to believe the model has worked properly...
I will test with the other flux sites.

First we test for Ha1 which has the longest time series.

Extract the data:

```{r Netcdf Manipulation Ha1}

name = "US-Ha1_1992-2012_FLUXNET2015_"

Met = nc_open(paste0(name,"Met.nc"))
Flux = nc_open(paste0(name,"Flux.nc"))

time = ncvar_get(Met,"time")
Tair = ncvar_get(Met,"Tair")
Precip = ncvar_get(Met,"Precip")
VPD = ncvar_get(Met,"VPD")
NEE = ncvar_get(Flux,"NEE")

ncatt_get(Met, "time")
time_from = substr(ncatt_get(Met, "time")$units, 15, 33)
time <- as.POSIXct(time, origin=time_from)

nc_close(Met)
nc_close(Flux)

# Define unit conversions
SEC_TO_30MIN = 1800
KEL_TO_CEL = -273.15

# Create data frame with the units converted
# Precip is now in mm
# Tair is now in Celsius
df <- data.frame(time, NEE, Tair+KEL_TO_CEL,Precip*SEC_TO_30MIN,VPD)
colnames(df)<- c("time","NEE","Tair","Precip","VPD")


df_day <- df %>%
      mutate(day=as.Date(time, format="%Y-%m-%d")) %>%
      group_by(day) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))

df_month <- df_day %>%
      mutate(month=format(as.Date(df_day$day),"%Y-%m")) %>%
      group_by(month) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))


# Create the NEE input matrix

df_day$Year = format(df_day$day,"%Y")
NEE = aggregate(df_day['NEE'],by=df_day['Year'],sum)
NEE$YearID = 1:nrow(NEE)

# Create our Precip input matrix
Precip = data.frame(NEE$Year,matrix(df_month$Precip,ncol = 12, byrow = TRUE))
colnames(Precip) <- c("Year","ppt1","ppt2","ppt3","ppt4","ppt5","ppt6","ppt7","ppt8","ppt9","ppt10","ppt11","ppt12")
```
Run the model for Ha1


```{r}
source("SAMFunction.R")
block = matrix(1:36,nrow=3,byrow=TRUE)
Nlag = 3
# For the timeblock created, run the model
SAM(NEE[-(1:3),],Precip,Nlag,block,prior=FALSE)
```
And we now plot it

```{r}
load("SAM_posterior_3_36_20200330_121002.Rdata")
NPPobs = data.frame(Year=1:nrow(NEE)+1992,
                    NPP_obs = NEE[,2])
NPPmod = data.frame(Year=1:length(SAM_posterior_3_36_20200330_121002$NPPmod$mean)+1995,
                    NPP_mod = SAM_posterior_3_36_20200330_121002$NPPmod$mean,
                    NPP_modmin = SAM_posterior_3_36_20200330_121002$NPPmod$min,
                    NPP_modmax = SAM_posterior_3_36_20200330_121002$NPPmod$max)
plot3 <- ggplot(NPPobs) +
  geom_line(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2) +
  geom_point(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2,na.rm=TRUE) +
  geom_ribbon(data=NPPmod, aes(x=Year, ymin=NPP_modmin, ymax=NPP_modmax), fill="grey70", alpha=0.4) +
  geom_line(data=NPPmod,aes(Year,NPP_mod)) +
  theme_bw() +
  theme(axis.line=element_line(colour = "black"),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    panel.background=element_blank()) 

# Assemble the dataframe for spring/non-spring
plotWeights = data.frame("Weights"=as.vector(t(SAM_posterior_3_36_20200330_121002$monthlyWeights$mean)),
                         "YearIntoPast"=rep(0:2,each=12),
                         "Month"=rep(c("Dec","Nov","Oct","Sep", "Aug","Jul",
                                       "Jun", "May","Apr","Mar","Feb","Jan"),3))
# Assign the factors
plotWeights$Month = factor(plotWeights$Month, levels = c("Jan","Feb","Mar","Apr",
                                                         "May","Jun","Jul","Aug",
                                                         "Sep","Oct","Nov","Dec"))
# Create plot ready for grid.assign
plot1 <- ggplot(plotWeights,aes(x=YearIntoPast,y=Weights,fill=Month)) +
      geom_bar(stat="identity", position=position_dodge(), linetype = "solid",size=0.5,color="black") +
      facet_grid(.~YearIntoPast,scales = "free_x",switch = "x", space = "free_y") +
      ggtitle(paste0("3 year lag, spring/non-spring (R2 = ",
                     signif(SAM_posterior_3_36_20200330_121002$R2,2), ", DIC = ",
                     signif(SAM_posterior_3_36_20200330_121002$DIC,4), ", MAE = ",
                     signif(SAM_posterior_3_36_20200330_121002$MAE,4),")"))
grid.arrange(plot1, plot3)
```

The monthly weights are super whack and are way too precise/noisy to logically be 
accepted as modelling a physical relationship - this is fitting to noise as Gab
said, I believe.

One last test, we model the Var data set...

```{r Netcdf Manipulation Var}

name = "US-Var_2001-2014_FLUXNET2015_"

Met = nc_open(paste0(name,"Met.nc"))
Flux = nc_open(paste0(name,"Flux.nc"))

time = ncvar_get(Met,"time")
Tair = ncvar_get(Met,"Tair")
Precip = ncvar_get(Met,"Precip")
VPD = ncvar_get(Met,"VPD")
NEE = ncvar_get(Flux,"NEE")

ncatt_get(Met, "time")
time_from = substr(ncatt_get(Met, "time")$units, 15, 33)
time <- as.POSIXct(time, origin=time_from)

nc_close(Met)
nc_close(Flux)

# Define unit conversions
SEC_TO_30MIN = 1800
KEL_TO_CEL = -273.15

# Create data frame with the units converted
# Precip is now in mm
# Tair is now in Celsius
df <- data.frame(time, NEE, Tair+KEL_TO_CEL,Precip*SEC_TO_30MIN,VPD)
colnames(df)<- c("time","NEE","Tair","Precip","VPD")


df_day <- df %>%
      mutate(day=as.Date(time, format="%Y-%m-%d")) %>%
      group_by(day) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))

df_month <- df_day %>%
      mutate(month=format(as.Date(df_day$day),"%Y-%m")) %>%
      group_by(month) %>%               # group by the day column
      summarise(NEE=sum(NEE),Tair=mean(Tair),Precip=sum(Precip),VPD=mean(VPD))


# Create the NEE input matrix

df_day$Year = format(df_day$day,"%Y")
NEE = aggregate(df_day['NEE'],by=df_day['Year'],sum)
NEE$YearID = 1:nrow(NEE)

# Create our Precip input matrix
Precip = data.frame(NEE$Year,matrix(df_month$Precip,ncol = 12, byrow = TRUE))
colnames(Precip) <- c("Year","ppt1","ppt2","ppt3","ppt4","ppt5","ppt6","ppt7","ppt8","ppt9","ppt10","ppt11","ppt12")
```

Run the model:
```{r}
source("SAMFunction.R")
block = matrix(1:36,nrow=3,byrow=TRUE)
Nlag = 3
# For the timeblock created, run the model
SAM(NEE[-(1:3),],Precip,Nlag,block,prior=FALSE)
```

and finally, plot the results:

```{r}
load("SAM_posterior_3_36_20200330_124141.Rdata")
NPPobs = data.frame(Year=1:nrow(NEE)+2001,
                    NPP_obs = NEE[,2])
NPPmod = data.frame(Year=1:length(SAM_posterior_3_36_20200330_124141$NPPmod$mean)+2004,
                    NPP_mod = SAM_posterior_3_36_20200330_124141$NPPmod$mean,
                    NPP_modmin = SAM_posterior_3_36_20200330_124141$NPPmod$min,
                    NPP_modmax = SAM_posterior_3_36_20200330_124141$NPPmod$max)
plot3 <- ggplot(NPPobs) +
  geom_line(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2) +
  geom_point(data=NPPobs,aes(Year,NPP_obs),color='steelblue',size=2,na.rm=TRUE) +
  geom_ribbon(data=NPPmod, aes(x=Year, ymin=NPP_modmin, ymax=NPP_modmax), fill="grey70", alpha=0.4) +
  geom_line(data=NPPmod,aes(Year,NPP_mod)) +
  theme_bw() +
  theme(axis.line=element_line(colour = "black"),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    panel.background=element_blank()) 

# Assemble the dataframe for spring/non-spring
plotWeights = data.frame("Weights"=as.vector(t(SAM_posterior_3_36_20200330_124141$monthlyWeights$mean)),
                         "YearIntoPast"=rep(0:2,each=12),
                         "Month"=rep(c("Dec","Nov","Oct","Sep", "Aug","Jul",
                                       "Jun", "May","Apr","Mar","Feb","Jan"),3))
# Assign the factors
plotWeights$Month = factor(plotWeights$Month, levels = c("Jan","Feb","Mar","Apr",
                                                         "May","Jun","Jul","Aug",
                                                         "Sep","Oct","Nov","Dec"))
# Create plot ready for grid.assign
plot1 <- ggplot(plotWeights,aes(x=YearIntoPast,y=Weights,fill=Month)) +
      geom_bar(stat="identity", position=position_dodge(), linetype = "solid",size=0.5,color="black") +
      facet_grid(.~YearIntoPast,scales = "free_x",switch = "x", space = "free_y") +
      ggtitle(paste0("3 year lag, spring/non-spring (R2 = ",
                     signif(SAM_posterior_3_36_20200330_124141$R2,2), ", DIC = ",
                     signif(SAM_posterior_3_36_20200330_124141$DIC,4), ", MAE = ",
                     signif(SAM_posterior_3_36_20200330_124141$MAE,4),")"))
grid.arrange(plot1, plot3)
```
This maps almost perfectly again. 

The key issue bothering me is just how perfect the fit is. I will start over D: 

It is possible that I need to add temperature and VPD - perhaps with such short
time series and only one variable, it is too easy for the model to just 
assign weights that fit well.

A quick test of running the model as a prior has shown what we expect regarding 
monthly and yearly weights (all roughly equal) and SD for the model.

***
# Thoughts

* Is it possible to consider lags in NEE explaining NEE - consider correlation of
the productivity measure and whether this has influence on itself.

* The model code contains the weight for each month, normalised to that years
contribution (it is the alphas at the end of the code) - this might be useful
to show that spring is clearly the most important.